---
title: "Reproducible data"
author: "Nikita"
date: "21/06/2020"
output: html_document
---

#Load the file

```{r}
data <- read.csv("activity.csv")
date <- data$date
steps <- data$steps
interval <- data$interval
date <- as.POSIXct(date)
steps <- steps[!is.na(steps)]
```

#Calculate the total number of steps taken per day and plot histogram

```{r}
steps_per_day <- with(data, tapply(steps, as.factor(data$date), sum, na.rm = TRUE))
hist(steps_per_day)
```

#Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean_median <- summary(steps_per_day)
mean_median
```

#A time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
steps_by_interval <- aggregate(steps ~ interval, data, mean)
plot(steps_by_interval$interval,steps_by_interval$steps, type="l", xlab="Interval", ylab="Number of Steps",main="Average Number of Steps per Day by Interval")

```

#Maximum number of steps interval

```{r}
max <- steps_by_interval[which.max(steps_by_interval$steps),1]
max
```

#Calculate and report the total number of missing values in the dataset

```{r}
Total_Nas <- sum(!complete.cases(data))
Total_Nas
```

#Using Mean for the day compute missing values

```{r}
Average_Steps <- aggregate(steps ~ interval, data = data, FUN = mean)
Nas <- numeric()
for (i in 1:nrow(data)) {
    obs <- data[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(Average_Steps, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    Nas <- c(Nas, steps)
}
```

#Create a new dataset including the imputed missing values

```{r}
new_activity <- data
new_activity$steps <- Nas
```

# Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.

```{r}
par(mfrow=c(2,1))
hist(Average_Steps$steps, xlab="steps",ylab="Frequency",
     main="Data with NA's filled in",border='green',col="skyblue")
hist(steps_per_day, xlab="steps",ylab="Frequency",
     main="NA's not filled in",border='purple',col="gray70",)
```

#mean and median total number of steps taken per day

```{r}
summary(Average_Steps$steps)
```

#
```{r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", 
              "Friday")
new_activity$dow = as.factor(ifelse(is.element(weekdays(as.Date(new_activity$date)),weekdays), "Weekday", "Weekend"))
StepsTotalUnion <- aggregate(steps ~ interval + dow, new_activity, mean)
library(lattice)
xyplot(StepsTotalUnion$steps ~ StepsTotalUnion$interval|StepsTotalUnion$dow, main="Average Steps per Day by Interval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")
```

